Building Sustainable Software - The CSDMS Approach

### 2014-07-14 paper.tex
Minor changes.

\title[]{Building Sustainable Software - The CSDMS-2.0 Approach}

@@

The Community Surface Dynamics Modeling System (\csdms{}) is an NSF funded
project whose focus is to aid a diverse community of earth and ocean system
model \emph{users} and \emph{developers} to use and create robust software
quickly.  To this end, \csdms{} develops, integrates, archives and disseminates
earth-system models and tools to an international (67 country) community
with the goal of building the set of tools necessary to model the
earth system. \csdms is a place modelers look to for access to hundreds open
source surface-dynamics models and tools, as well as model metadata. Such a
model repository increases model transparency and helps to eliminate the
duplication of effors by presenting the current state of modeling efforts.
To increase software sustainability, composability and interoperability \csdms
promotes standards that define common modeling interfaces, semantic mediation
between models, and model metadata. Through online resources and workshops,
\csdms promotes software engineering best practices, which are foreign to many
developers within our modeling community. For example, version control, unit
testing, continious integration, test-driven development, well-written
\emph{clean code} are all topics of the educational mission of \csdms{}.

@@

The mission of the Community Surface Dynamics Modeling System (\csdms{})
~\cite{peckham2012component} is to help a diverse modeling community toward
common goals and standards.
%The Community Surface Dynamics Modeling System (\csdms{})
%is an NSF-funded project that began in 2007. Its mission is to help a diverse
%community of surface dynamics model \emph{developers} and model \emph{users}
%work together toward
%common goals and standards.
This effort involves creating:
\begin{itemize}
  \item a repository of source code and metadata for open-source models and
    tools (section~\ref{sec:organizing})
  \item reusable plug-and-play model components and a framework
        within which these components can be coupled to create new models
        (section~\ref{sec:reusable})
  \item an efficient and open modeling community through education and
        standards (section~\ref{sec:education})
\end{itemize}

@@

\csdms{} has developed innovative model/component interfaces that promote
model reuse and interoperability,
including the Basic Model Interface (\bmi{} - section~\ref{sec:bmi}), which
uses
the \csdms{} Standard Names (section~\ref{sec:standardnames}) and a framework
within which models can be coupled and enhanced with a set of \bmi{}-compatible
service components.
%Component Model Interface (CMI).
The \csdms{} Web Modeling Tool (\wmt{} - section~\ref{sec:wmt}) is a web-based client that provides a
graphical interface to this framework and allows users to compose new models
by connecting and configuring components in a simple, browser-based graphical
interface.

@@

\subsection{Sustainability through standards}

@@

\subsubsection{CSDMS Standard Names}
\label{sec:standardnames}

@@

\subsection{Connecting and running models through the web}
\label{sec:wmt}

@@

\section{Education and Evaluation of \csdms{} tools}
\label{sec:education}

@@

\section{Summary: Building an active and efficient Modeling Community}

>>>>

\title[]{Building Sustainable Software - The CSDMS Approach}

@@

\csdms, The Community Surface Dynamics Modeling System, is an NSF funded
project whose focus is to aid a diverse community of earth and ocean system
model \emph{users} and \emph{developers} to use and create robust software
quickly.  To this end, \csdms{} develops, integrates, archives and disseminates
earth-system models and tools to an international (67 country) community
with the goal of building the set of tools necessary to model the
earth system. \csdms{} is a place modelers look to for access to hundreds open
source surface-dynamics models and tools, as well as model metadata. Such a
model repository increases model transparency and helps to eliminate the
duplication of effors by presenting the current state of modeling efforts.
To increase software sustainability, composability and interoperability \csdms{}
promotes standards that define common modeling interfaces, semantic mediation
between models, and model metadata. Through online resources and workshops,
\csdms{} promotes software engineering best practices, which are foreign to many
developers within our modeling community. For example, version control, unit
testing, continious integration, test-driven development, well-written
\emph{clean code} are all topics of the educational mission of \csdms{}.

@@

The mission of the Community Surface Dynamics Modeling System (\csdms{})
~\cite{peckham2012component} is to help a diverse modeling community toward
common goals and standards.
%The Community Surface Dynamics Modeling System (\csdms{})
%is an NSF-funded project that began in 2007. Its mission is to help a diverse
%community of surface dynamics model \emph{developers} and model \emph{users}
%work together toward
%common goals and standards.
This effort involves creating:
\begin{itemize}
  \item a repository of source code and metadata for open-source models and
    tools (Section~\ref{sec:organizing})
  \item reusable plug-and-play model components and a framework
        within which these components can be coupled to create new models
        (Section~\ref{sec:reusable})
  \item an efficient and open modeling community through education and
        standards (Section~\ref{sec:education})
\end{itemize}

@@

\csdms{} has developed innovative model/component interfaces that promote
model reuse and interoperability,
including the Basic Model Interface (\bmi{} - Section~\ref{sec:bmi}), which
uses
the \csdms{} Standard Names (Section~\ref{sec:standardnames}) and a framework
within which models can be coupled and enhanced with a set of \bmi{}-compatible
service components.
%Component Model Interface (CMI).
The \csdms{} Web Modeling Tool (\wmt{} - Section~\ref{sec:wmt}) is a web-based client that provides a
graphical interface to this framework and allows users to compose new models
by connecting and configuring components in a simple, browser-based graphical
interface.

@@

\subsection{Sustainability and Interoperability Through Standards}

@@

\subsubsection{\csdms{} Standard Names}
\label{sec:standardnames}

@@

\subsection{Connecting and Running Models Through the Web}
\label{sec:wmt}

@@

\section{Education and Evaluation of \csdms{} Tools}
\label{sec:education}

@@

\section{Summary: Building an active and efficient modeling community}
